Well-quasi-orderings on word languages

### 2024-08-19 src/infixes.tex
typo

\begin{lemma}
    \label{chains-infix:lem}
    Let $L$ be a \kl{chain} for the \kl{infix relation}. Then, there exists
    a \kl{chain} $P$ for the \kl{prefix relation} and a \kl{chain}
    $S$ for the \kl{suffix relation} such that $L \subseteq SP$.
\end{lemma}
\begin{proof}
    Because $L$ is a chain,
    we have an enumeration $L = \seqof{w_n}$,
    where $s_n \defined \card{w_n}$ is increasing, 
    and functions
    $f_{i,j} \colon \set{1, \dots, s_i} \to \set{1, \dots s_{j}}$
    satisfying
    that $f_{j,k} \circ f_{i, j} = f_{i, k}$,
    $f_{i,i} = \mathrm{id}$, and
    $w_i = w_j[f_{i,j}(1):f_{i,j}(s_i)]$ for all $i \leq j$.
    Now, we can build the infinite word $w_\infty$ indexed by $\Zel$, and
    embeddings $f_{i, \infty} \colon \set{1, \dots, s_i} \to \Rel$ such that
    $w_i = w_\infty[f_{i, \infty}(1):f_{i, \infty}(s_i)]$, and $f_{i, \infty}
    \circ f_{j, i} = f_{j, \infty}$ for all $i \leq j$.

>>>>

\begin{lemma}
    \label{chains-infix:lem}
    Let $L$ be a \kl{chain} for the \kl{infix relation}. Then, there exists
    a \kl{chain} $P$ for the \kl{prefix relation} and a \kl{chain}
    $S$ for the \kl{suffix relation} such that $L \subseteq SP$.
\end{lemma}
\begin{proof}
    Because $L$ is a chain,
    we have an enumeration $L = \seqof{w_n}$,
    where $s_n \defined \card{w_n}$ is increasing, 
    and functions
    $f_{i,j} \colon \set{1, \dots, s_i} \to \set{1, \dots s_{j}}$
    satisfying
    that $f_{j,k} \circ f_{i, j} = f_{i, k}$,
    $f_{i,i} = \mathrm{id}$, and
    $w_i = w_j[f_{i,j}(1):f_{i,j}(s_i)]$ for all $i \leq j$.
    Now, we can build the infinite word $w_\infty$ indexed by $\Rel$, and
    embeddings $f_{i, \infty} \colon \set{1, \dots, s_i} \to \Rel$ such that
    $w_i = w_\infty[f_{i, \infty}(1):f_{i, \infty}(s_i)]$, and $f_{i, \infty}
    \circ f_{j, i} = f_{j, \infty}$ for all $i \leq j$.
